---
title: "Inconsistencies between methods"
author: "JM"
output: pdf_document
---

```{r, echo=FALSE, message=FALSE} 
library(knitr)
library(dplyr)
mapping = read.csv("inconsistent_methods.csv")
```

### Serogroups that JM has that PB doesn't

The following are those that JM has that PB doesn't have

```{r, comment=''}
mapping %>% filter(jm & !pb) %>% select(-jm, -pb) %>% arrange(-abundance) %>% kable
```

By the looks the reason they're still legitimate is due to:

1. PB got it wrong (it seems the cluster names might not be right?)
2. They're high abundance (so unlikely to be errors)
3. They're low abundance, and the closest serogroup is not very abundant.

### Serogroups that PB has that JM doesn't

The following are those that PB has that JM hasn't

```{r, comment=''}
mapping %>% filter(pb & !jm) %>% select(-jm, -pb) %>% arrange(-abundance) %>% kable
```

These are universally low abundance, and close to a serogroup with high abundance.

### All serogroups

```{r, comment=''}
mapping %>% arrange(-abundance) %>% kable
```