---
title: "Inconsistencies between methods"
author: "JM"
output: pdf_document
---

```{r, echo=FALSE, message=FALSE} 
library(knitr)
library(dplyr)
mapping = read.csv("temp/inconsistent_methods.csv")
```

### Serogroups that JM has that PB doesn't

The following are those that JM has that PB doesn't have

```{r, comment=''}
mapping %>% filter(jm & !pb) %>% select(-jm, -pb) %>% arrange(-abundance) %>% kable
```

By the looks the reason they're still legitimate is due to:

1. They're high abundance (so unlikely to be errors)
2. They're low abundance, and the closest serogroup is not abundant enough to produce this
many errors (given the estimated error rate).

### Serogroups that PB has that JM doesn't

The following are those that PB has that JM hasn't

```{r, comment=''}
mapping %>% filter(pb & !jm) %>% select(-jm, -pb) %>% arrange(-abundance) %>% kable
```

These are universally low abundance, and close to a serogroup with high abundance.

### All serogroups

```{r, comment=''}
mapping %>% arrange(-abundance) %>% kable
```