---
title: "Inconsistencies between methods"
author: ""
output: pdf_document
---

```{r, echo=FALSE, message=FALSE} 
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
mapping = read.csv("temp/inconsistent_methods.csv")
```

### Serogroups that the EC-method has that CD-Hit doesn't

The following are those gST types that the error correction method has that CD-Hit doesn't have

```{r, comment=''}
mapping %>% filter(jm & !pb) %>% select(-jm, -pb) %>% arrange(-abundance) %>% kable
```

By the looks the reason they're still legitimate is due to:

1. They're high abundance (so unlikely to be errors)
2. They're low abundance, and the closest serogroup is not abundant enough to produce this
many errors (given the estimated error rate).

### Serogroups that CD-hit has that the EC-method doesn't

The following are those that CD-hit has that the error correct method doesn't have

```{r, comment=''}
mapping %>% filter(pb & !jm) %>% select(-jm, -pb) %>% arrange(-abundance) %>% kable
```

These are universally low abundance, and close to a serogroup with high abundance.

### All serogroups

```{r, comment=''}
mapping %>% rename(EC_method = jm, CD_hit = pb) %>% arrange(-abundance) %>% kable
```